\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-18 paper.tex
added

\begin{enumerate}
    \item \textbf{Subadditivity (SA)}: Entropy of combined system is at most the sum of information in the individual components.
    This property ensures redundancy exists when storing information across multiple locations. This means potential information overlaps between components, which ensures recovery mechanisms.
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=\textwidth]{subadditivity.jpeg}  % Adjust width as needed
        \caption{The red line value has to be less than or equal to the sum of orange line values in order to ensure subadditivity.}  % Caption text
        \label{fig:Subadditivity}  % Label for referencing
    \end{figure}
    \\
    We can illustrate this property on our example from above (Fig. 3).
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=\textwidth]{SA_ex.jpeg}  % Adjust width as needed
        \caption{In this example property 1 holds. Therefore, edge weight for AB is valid!}  % Caption text
        \label{fig:Subadditivity Example}  % Label for referencing
    \end{figure}

@@

\section{Holographic Quantum State}
\hspace{0.5cm} All boundary states in CFT are holographic. Because of this, there is a corresponding interpretation in bulk AdS space. This allows us to perform computations on a lower-dimensional bounday with no gravity, which then gives us information about higher-dimensional gravity in bulk space, like I stated above (1.3 Holographic Principle). 
\\
But in order for holographic quantum state to be valid it \textbf{must} satisfy the following property:
\vspace{0.3cm}
\\\textbf{Monogamy of Mutual Information (MMI)}: 
\[
S(AB) + S(BC) + S(AC) \geq S(A) + S(B) + S(C) + S(ABC)
\]

>>>>

\begin{enumerate}
    \item \textbf{Subadditivity (SA)}: Entropy of combined system is at most the sum of information in the individual components.
    This property ensures redundancy exists when storing information across multiple locations. This means potential information overlaps between components, which ensures recovery mechanisms.
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=\textwidth]{sa.jpeg}  % Adjust width as needed
        \caption{The red line value has to be less than or equal to the sum of orange line values in order to ensure subadditivity.}  % Caption text
        \label{fig:Subadditivity}  % Label for referencing
    \end{figure}
    \\
    We can illustrate this property on our example from above (Fig. 3).
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=\textwidth]{SA_ex.jpeg}  % Adjust width as needed
        \caption{In this example property 1 holds. Therefore, edge weight for AB is valid!}  % Caption text
        \label{fig:Subadditivity Example}  % Label for referencing
    \end{figure}

@@

\section{Holographic Quantum State}
\hspace{0.5cm} All boundary states in CFT are holographic. Because of this, there is a corresponding interpretation in bulk AdS space. This allows us to perform computations on a lower-dimensional bounday with no gravity, which then gives us information about higher-dimensional gravity in bulk space, like I stated above (1.3 Holographic Principle). 
\\
But in order for a holographic quantum state to be valid it \textbf{must} satisfy the following property:
\vspace{0.3cm}
\\\textbf{Monogamy of Mutual Information (MMI)}: 
\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=\textwidth]{mmi.jpeg}  % Adjust width as needed
    \caption{This illustration represents the property of MMI in the boundary/ bulk. Where S(AC) = S(A U C)}  % Caption text
    \label{fig:mmi}  % Label for referencing
\end{figure}
